\section{Datasets}
Before proceeding to a discussion of the preprocessing of the datasets, it is necessary to inform readers that changes have been made to two of the datasets originally proposed.\\\newline
The first change refers to the Pennsylvania dataset.
The decision was made to replace the original Pennsylvania road network dataset with the corresponding dataset from \cite{Pennsylvania}.
The decision to replace the undirected dataset with a directed one was made to ensure greater uniformity among road networks.\\\newline
The second change refers to the Twitch dataset.
Due to concerns regarding the large number of edges in the original dataset during the initial experimental phase, it has been replaced with a smaller Deezer dataset from \cite{Deezer}. \\\newline
Furthermore, the two "Mus Musculus" and "Saccharomyces cerevisiae" datasets are described in greater detail as follows.
Both of them have been downloaded from the STRING Database \cite{STRING}, filtered with the following options: a confidence score of $>0.4$ for Mus Musculus and $>0.7$ for Saccharomyces cerevisiae; and only AB pairs (undirected). \\\newline
The subsequent table has been revised to reflect the aforementioned modifications. These alterations can be discerned within the table itself, as they are highlighted.
\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        \textbf{\scalebox{0.87}{\large{Network}}} & \scalebox{0.87}{\large$\bm{|V|}$} & \scalebox{0.87}{\large$\bm{|E|}$} & \textbf{\scalebox{0.87}{\large{Type}}} \\
        \hline
        Pennsylvania \cite{PennsylvaniaSource,Pennsylvania} & \textcolor{red}{1,088,092} & \textcolor{red}{3,083,796} & \textcolor{red}{Directed} \\
        \hline
        Padua (province) \cite{padua2025} & 122,680 & 304,184 & Directed \\
        \hline
        Hong Kong (city) \cite{hongkong2025} & 43,620 & 91,542 & Directed \\
        \hline
        Italian Covid-19 Retweet Network \cite{mesina2024italian} & 221,574 & 800,000 & Directed \\
        \hline
        \textcolor{red}{Deezer} \cite{DeezerSource,Deezer} & \textcolor{red}{143,884} & \textcolor{red}{846,915} & Undirected \\
        \hline
        GitHub Developers \cite{GitHubSource,GitHub} & 37,700 & 289,003 & Undirected \\
        \hline
        Mus Musculus Protein Interactions \cite{STRING} & 20,969 & 800,000 & Undirected \\
        \hline
        Saccharomyces cerevisiae Protein Interactions \cite{STRING} & 5,786 & 100,000 & Undirected \\
        \hline
        Bio-grid-fission-yeast \cite{nr} & 2,000 & 25,300 & Undirected \\
        \hline
    \end{tabular}
    \caption{Datasets used in the project}
    \label{tab:datasets}
\end{table}
\\
A preprocessing pipeline is utilized in which all datasets are converted into CSV files and only the useful features are extracted, if present.\\\newline
Initially, all the datasets were manually converted to CSV files, as some of them were not directly available in this format.
Subsequently, a Python script was implemented to automate the following preprocessing of the datasets.
Undirected edges $(u, v)$ are represented using a pair of directed edges $(u, v)$ and $(v, u)$.
Unweighted datasets are represented as having a uniform weight of $1.0$ for all edges. 
Finally, the node IDs are mapped to numeric consecutive IDs, with the sequence beginning at $0$. 