\section{Datasets}
Before proceeding to a discussion of the preprocessing of the datasets, it is necessary to inform readers that changes have been made to the Pennsylvania dataset in the proposal.
The dataset from \cite{snapnets} has been used instead.
The decision to change the dataset was made to have a directed graph, instead of an undirected one, so to have more uniformity among road networks. \\\newline
Due to concerns about the large number of edges of the Twitch dataset during the first experiments, it has been replaced with a smaller Deezer dataset from \cite{Deezer}. \\\newline
We also want to provide more information about the two "Mus Musculus" and "Saccharomyces cerevisiae" datasets. Both of them have been downloaded
from the STRING Database \cite{STRING}, filtered with the following options: $>0.4$ confidence score for Mus Musculus, $>0.7$ for Saccharomyces cerevisiae; only AB pairs (undirected). \\\newline
What follows is the complete updated table (changes highlighted):
\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        \textbf{\scalebox{0.87}{\large{Network}}} & \scalebox{0.87}{\large$\bm{|V|}$} & \scalebox{0.87}{\large$\bm{|E|}$} & \textbf{\scalebox{0.87}{\large{Type}}} \\
        \hline
        Pennsylvania \cite{Pennsylvania} & \textcolor{red}{1,088,092} & \textcolor{red}{3,083,796} & \textcolor{red}{Directed} \\
        \hline
        Padua (province) \cite{padua2025} & 122,680 & 304,184 & Directed \\
        \hline
        Hong Kong (city) \cite{hongkong2025} & 43,620 & 91,542 & Directed \\
        \hline
        Italian Covid-19 Retweet Network \cite{mesina2024italian} & 221,574 & 800,000 & Directed \\
        \hline
        \textcolor{red}{Deezer} \cite{Deezer} & \textcolor{red}{143,884} & \textcolor{red}{846,915} & Undirected \\
        \hline
        GitHub Developers \cite{rozemberczki2019multiscale} & 37,700 & 289,003 & Undirected \\
        \hline
        Mus Musculus Protein Interactions \cite{STRING} & 20,969 & 800,000 & Undirected \\
        \hline
        Saccharomyces cerevisiae Protein Interactions \cite{STRING} & 5,786 & 100,000 & Undirected \\
        \hline
        Bio-grid-fission-yeast \cite{nr} & 2,000 & 25,300 & Undirected \\
        \hline
    \end{tabular}
    \caption{Datasets used in the project}
    \label{tab:datasets}
\end{table}
\\
A preprocessing pipeline is employed where all datasets are converted into CSV files and only useful features 
are kept, if present. Undirected edges $(u, v)$ are represented using a pair of directed edges $(u, v)$ and $(v, u)$.
Unweighted datasets are represented as having a uniform weight of 1.0 for all edges. Finally, if the node IDs are not numeric, they 
are mapped to numeric consecutive IDs starting from 0. The Python script that performs this preprocessing step is available
in the project's Github repository.